---
title: "hw2"
author: "Tianyi Wang"
date: "2017Äê9ÔÂ26ÈÕ"
output: html_document
---

#Chp3.4
##(a)

The prior distribution of p0 and p1 is Beta(1,1).
The posterior distribution: p0: Beta(40,636); p1: Beta(23,659).
We sample 1000 points from those distributions.

```{r,warning=FALSE}
alpha0=1+39
beta0=1+674-39
alpha1=1+22
beta1=1+680-22
p0=rbeta(1000,alpha0,beta0)
p1=rbeta(1000,alpha1,beta1)
par(mfrow=c(1,2))
hist(p0,main ="simulations of p0")
hist(p1,main ="simulations of p1")
```

##(b)

```{r}
odds.ratio=(p1/(1-p1))/(p0/(1-p0))
odds.ratio.PI <- quantile(odds.ratio, c(.025, .975))
odds.ratio.PI # 95% posterior probability interval
hist(odds.ratio,breaks = 50); abline(v=odds.ratio.PI,lty=2)
```


#Chp3.11
##(a)

```{r}
library(boot)
x=c(-0.863,-0.296,-0.053,0.727)
n=c(5,5,5,5)
y=c(0,1,3,5)
#prior
prior<-function(a,b){
  p=exp(-1/1.5*(a^2/4+(b-10)^2/100-a*(b-10)/20))
  return(p)
}
#likelihood
likelihood=function(a,b){
  l=1
  for (i in 1:4){
    theta <- inv.logit(a + b*x[i])
    l=l*theta^(y[i])*(1-theta)^(n[i]-y[i])
  }
  return(l)
}
#posterior density
posterior.density=function(a,b){
  pri=prior(a,b)
  llh=likelihood(a,b)
  posterior=pri*llh
  return(posterior)
}
a=seq(-4,8,0.05)
b=seq(-5,45,0.2)
produce.coutour=function(fct){
  matrix=matrix(1,length(a),length(b))
  for (i in (1:length(a))){
    matrix[i,]=fct(a[i],b)
  }
  return(matrix)
}
z=produce.coutour(posterior.density)
par(mfrow=c(1,1))
contour(a,b,z, nlevels=21,xlim=c(-3,4),ylim=c(0,30),xlab="alpha",ylab="beta",drawlabels=F)
title("The contour plot of the posterior distribution")
```


```{r}
delta <- (a[2] - a[1]) / 2
epsilon <- (b[2] - b[1]) / 2
posterior.a <- apply(z, 1, sum)  # marginal posterior for alpha
alpha.sim <- rep(NA, 1000)
beta.sim <- rep(NA, 1000)
for(s in 1:1000){
  i <- sample(length(a), 1, prob=posterior.a)
  j <- sample(length(b), 1, prob=z[i,])
  alpha.sim[s] <- a[i] + runif(1, -delta,  delta)
  beta.sim[s] <- b[j] + runif(1, -epsilon, epsilon)
}
plot(alpha.sim, beta.sim)
title(" scatterplot of 1000 random draws from the posterior")
```

```{r}
index=which(beta.sim>0)
#index=1000
LD50.sim <- -alpha.sim / beta.sim
LD50.PI <- quantile(LD50.sim, c(.025, .975))
LD50.PI # 95% posterior probability interval
hist(LD50.sim, breaks=30); abline(v=LD50.PI, lty=2);
```


##(b)
```{r}
#prior contour
prior.z=produce.coutour(prior)
#likelihood contour
llh.z=produce.coutour(likelihood)
par(mfrow=c(2,2))
contour(a,b,prior.z,nlevels=21,xlim=c(-3,4),ylim=c(0,30),xlab="alpha",ylab="beta",drawlabels=F)
title("The contour plot of the prior distribution")
contour(a,b,llh.z, nlevels=15,xlim=c(-3,4),ylim=c(0,30),xlab="alpha",ylab="beta",drawlabels=F)
title("The contour plot of the likelihood")
contour(a,b,z, nlevels=15,xlim=c(-3,4),ylim=c(0,30),xlab="alpha",ylab="beta",drawlabels=F)
title("The contour plot of the posterior distribution")
```

The scatterplot is a compromise between the prior distribution and the likelihood.

##(c)

The prior information decides a scope where the posterior will mainly be located. But the power of likelihood is stronger.

#Chp3.12
##(e)

```{r}
data1=read.csv("C://Users//Think//Documents//data.csv")
y=data1$Fatal.accidents
t=data1$Year-1975
m1=lm(y~t)
a=as.numeric(m1$coefficients[1])
b=as.numeric(m1$coefficients[2])
```

**crude estimates:**
```{r}
c(a,b)
```

**uncertainties / standard deviations :**
```{r}
c(2.7494,0.4431)
```


##(f)&(g)

```{r}
28.87+c(-5,5)*2.7494 #15,42
-0.9212+c(-5,5)*0.4431 #-3.14,1.29
posterior=function(y,t,a,b){
  p=1
  for (i in 1:nrow(data1)){
    m=a+b*t[i]
    p=p*m^y[i]*exp(-m)/factorial(y[i])
  }
  return(p)
}
a=seq(15,42,0.2)
b=seq(-3.14,1.29,0.02)
matrix=matrix(1,length(a),length(b))
for (i in (1:length(a))){
    for (j in (1:length(b))){
      xxx=(a[i]/12+b[j])<=0
      if (xxx==TRUE){
        matrix[i,j]=0
      } else{
        matrix[i,j]=posterior(y,t,a[i],b[j])
      }
    }
}
contour(a,b,matrix, nlevels=10,xlim=c(15,33),ylim=c(-2.8,1.3),xlab="alpha",ylab="beta",drawlabels = F)
title("The contour plot of the posterior distribution")
```



```{r}
delta <- (a[2] - a[1]) / 2
epsilon <- (b[2] - b[1]) / 2
posterior.a <- apply(matrix, 1, sum)  # marginal posterior for alpha
alpha.sim <- rep(NA, 1000)
beta.sim <- rep(NA, 1000)
posterior.mean=rep(0,1000)
for(s in 1:1000){
  i <- sample(length(posterior.a), 1, prob=posterior.a)
  j <- sample(length(b), 1, prob=matrix[i,])
  posterior.mean[s]=matrix[i,j]
  alpha.sim[s] <- a[i] + runif(1, -delta,  delta)
  beta.sim[s] <- b[j] + runif(1, -epsilon, epsilon)
}
plot(alpha.sim, beta.sim)
title(" scatterplot of 1000 random draws from the posterior")
```

```{r}
hist(posterior.mean,main="histogram of the posterior density for the expected
number of fatal accidents in 1986")
```

##(h)

```{r}
mean.sim <- alpha.sim+beta.sim*(1986-1976)
mean.PI <- quantile(mean.sim, c(.025, .975))
mean.PI # 95% posterior probability interval
hist(mean.sim, breaks=30); abline(v=mean.PI, lty=2);
```

#Chp4.1
##(b)

```{r}
first.dr=function(y,theta){
  f=sum(2*(y-theta)/(1+(y-theta)^2))
  return(f)
}
y=c(43, 44, 45, 46.5, 47.5)
theta=seq(0,100,1)
values=NULL
for(i in 1:length(theta)){
  values=c(values,first.dr(y,theta[i]))
}
plot(values~theta)
theta=seq(40,50,0.1)
values=NULL
for(i in 1:length(theta)){
  values=c(values,first.dr(y,theta[i]))
}
plot(values~theta)
theta=seq(44,46,0.001)
values=NULL
for(i in 1:length(theta)){
  values=c(values,first.dr(y,theta[i]))
}
print(paste("Posterior mode of theta",theta[which.min((values-0)^2)]))
```

##(c)

```{r}
theta=theta[which.min((values-0)^2)]
I=-sum(2*(-1+(y-theta)^2)/(1+(y-theta)^2)^2)
print(I)
print(1/I)
```

**¦È|y~N(44.862,0.727)**

```{r}
q=seq(42,48,0.02)
sample1=dnorm(q,44.862,0.727^0.5)
sample1=sample1/sum(sample1)
post=function(q){
  l=length(q)
  p=rep(0,l)
  for (i in 1:l){
    p[i]=prod(1/(1+(y-q[i])^2))
  }
  return(p)
}
sample2=post(q)
sample2=sample2/sum(sample2)
plot(q,sample1,type="l")
lines(q,sample2,col="red",lty=20)
legend(46,0.008,legend=c("normal","exact"),lty=19:20,col=1:2)
```

#Chp4.15
##(b)
**¦Ì|y~N(4/5*y,4/5)**
```{r}
(1+c(-1,1)*qnorm(0.75)*(4/5)^0.5)*5/4
```
**The coverage: P(0.496<=y<=2.004)**
**y|¦Ì=1~N(1,1)**
```{r}
pnorm(2.004,1,1)-pnorm(0.496,1,1)
```
****The coverage is 53.518%

##(c)
```{r}
mu0=seq(-5,8,0.05)
coverage=pnorm(2.004,mu0,1)-pnorm(0.496,mu0,1)
plot(coverage~mu0,type="l")
```